\documentclass[a4paper,10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in, top=-0.15in, bottom=0in, nomarginpar]{geometry}
\usepackage{chngcntr}
\usepackage{tabularx}
\usepackage[T1]{fontenc}% T1 is a much better choice of encoding than the default
\usepackage{fontawesome}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{array}
\usepackage{etoolbox}
\usepackage{colortbl}
\usepackage[svgnames]{xcolor}
\usepackage{makecell}
\usepackage{fontspec}
\usepackage{hyperref}

\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}

% Link colors
\hypersetup{%
  colorlinks,
  urlcolor={orange!80!black}
}


% Random settings
%\inputencoding{latin1}
\counterwithin{table}{section}
\pagenumbering{gobble} % switch off page numbers
\defaultfontfeatures{LetterSpace=-5} % less spacing between letters
\AtBeginEnvironment{flushleft}{\setmainfont{Montserrat}}%
\AtBeginEnvironment{flushright}{\setmainfont{Montserrat}}%
\AtBeginEnvironment{center}{\setmainfont{Montserrat}}%
\AtBeginEnvironment{tabularx}{\setmainfont{Montserrat}}%
\hyphenpenalty=10000 % no hyphenation

% Specify different font for section headings
\newfontfamily\headingfont[]{Montserrat Bold}
\titleformat*{\section}{\LARGE\headingfont}
\renewcommand{\maketitlehooka}{\headingfont}

% Macros for tables
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

% Macro for section titles + icon
% the trick here for minipage is: align the page to the baseline, then define the height (in pt), and then align the text inside to the top
\newcommand{\sectionTitle}[2]{\section*{#1 \hspace{1mm} {\Large \begin{minipage}[b][12.5pt][t]{3cm}#2\end{minipage}}}}

% Macro for the Personal Data table: icon + info
\newcommand{\personalData}[2]{#2 \hspace{0.7mm} #1}

% Macros for text formatting
\newcommand{\locationRight}[1]{\hfill {\footnotesize \textcolor{gray}{#1}}}

% Macro for vertical spacing
\newcommand{\vvv}{\vspace{4 mm}}



\begin{document}

% header section: title and subtitle
\title{{\Huge Curriculum Vitae} \\ {\large of} \\ {\Huge Fabrizio Ferrai}  \\ \vspace{2 mm} {\normalsize Software Engineer, Consultant}}
\predate{}
\postdate{}
\date{}
\preauthor{}
\postauthor{}
\author{}
\maketitle

% SECTION: PERSONAL DATA
\sectionTitle{Personal Data \& Contact}{\faPencil}

\noindent % needed if the tabularx environment isn't encased in a table environment
\begin{tabularx}{\textwidth}{ C{0.5cm} *{2}{X}}
	&
	\personalData{Location: Helsinki, Finland}{\faHome} &
	\personalData{Website: \href{https://ferrai.io}{ferrai.io}}{\faGlobe}
	\vspace{2 mm}\\
	&
	\personalData{Citizenship: Italian}{\faFlag} &
	\personalData{Github profile: \href{https://github.com/f-f}{github.com/f-f}}{\faGithubAlt}
	\vspace{2 mm}\\
	&
	\personalData{E-mail: \href{mailto:fabrizio@ferrai.io}{fabrizio@ferrai.io}}{\faEnvelope}
\end{tabularx}
\vspace{0 mm}

% SECTION: BIO
\sectionTitle{Short Bio}{\faUser}

\noindent
\large
\begin{tabularx}{\textwidth}{ L{18cm} }
	Curious being, hungry learner, keeping up the good vibes. Also, they say I make good pizza. \\
	Things I'm currently most interested in: \emph{Building Communities, Developer UX, DevOps, Software Architecture, Programming Languages for the Future}. \\
\end{tabularx}

\vspace{0 mm}

% SECTION: EXPERIENCE
\sectionTitle{Work Experience}{\faBriefcase}

\noindent
\large
\begin{tabularx}{\textwidth}{ C{0.5cm} L{4.0cm} *{1}{X}}
	& 2025 Nov -  & \textbf{IO Global Ltd} \locationRight{Remote} \vspace{1 mm}\\
	&			  & \hspace{5mm} {\normalsize \emph{Role:} Senior Software Engineer \vspace{0 mm}} \\
	&			  & \hspace{5mm} {\normalsize \emph{Tech:} Haskell \vspace{4 mm}} \\
	& 2021 Jan - 2025 Oct & \textbf{Norsk Video Streaming} \locationRight{Remote} \vspace{1 mm}\\
	&			  & \hspace{5mm} {\normalsize \emph{Role:} Senior Software Engineer \vspace{0 mm}} \\
	&			  & \hspace{5mm} {\normalsize \emph{Tech:} PureScript, Rust, Erlang, Zig, AWS \vspace{4 mm}} \\
  & 2019 Nov - 2021 Jan & \textbf{Santoru Ab - Freelance Software Engineer} \locationRight{Remote} \vspace{1 mm}\\
	&			  & \hspace{5mm} {\normalsize \emph{Notable clients:} \href{https://signalvine.com}{SignalVine}, \href{https://ksfmedia.fi}{KSF Media}, \href{https://condenast.com}{Condé Nast} \vspace{0 mm}} \\
	&			  & \hspace{5mm} {\normalsize \emph{Tech:} Haskell, PureScript, Dhall, Terraform, Kubernetes \vspace{4 mm}} \\
  & 2017 Jun - 2019 Nov & \textbf{KSF Media Ab} \locationRight{Helsinki, Finland} \vspace{1 mm}\\
	&			  & \hspace{5mm} {\normalsize \emph{Role:} Senior Software Engineer, Team Lead \vspace{0 mm}} \\
	&			  & \hspace{5mm} {\normalsize \emph{Tech:} Haskell, PureScript, Dhall, Terraform, Kubernetes \vspace{4 mm}} \\
  & 2011 - 2016 & \textbf{Freelance Software Engineer, Consultant} \locationRight{Remote} \vspace{1 mm}\\
	&			  & \hspace{5mm} {\normalsize \emph{Notable clients:} \href{http://sysdig.com}{Sysdig}, \href{http://algebris.it}{Algebris}, \href{http://helvar.com}{Helvar}, Nuvola, \href{https://elisa.fi}{Elisa} \vspace{0 mm}} \\
	&			  & \hspace{5mm} {\normalsize \emph{Tech:} Clojure/ClojureScript, Python, JS, PHP, Postgresql \vspace{0 mm}} \\
\end{tabularx}

\vspace{0 mm}

% SECTION: EDUCATION
\sectionTitle{Education}{\faBook}

\noindent
\large
\begin{tabularx}{\textwidth}{ C{0.5cm} L{3cm} *{1}{X}}
	& 2014 - 2022 & \textbf{Master} of Computer Science Engineering\locationRight{Aalto University, Finland} \vspace{3 mm}\\
	& 2011 - 2014 & \textbf{Bachelor} of Engineering of Computing Systems \locationRight{Politecnico di Milano, Italy} \vspace{3 mm}\\
	% &			  & \hspace{5mm} \emph{\normalsize Grade: 97/110 \vspace{3 mm}}\\
	& 2006 - 2011 & Science High School \textbf{Diploma} \locationRight{2nd Level College of Science "L. Mossa", Olbia, Italy} \vspace{3 mm}\\
	% &			  & \hspace{5mm} \emph{\normalsize Grade: 100/100 }\\
\end{tabularx}

% SECTION: PAPERS
%\sectionTitle{Academic Papers}{\faBeaker}
\newgeometry{margin=0.5in, top=0.5in, bottom=0in, nomarginpar}

% SECTION: PROGRAMMING
\sectionTitle{Programming \& Technologies}{\faMagic \hspace{0.5mm} \faLaptop}

\noindent
\large
\begin{tabularx}{\textwidth}{ C{0.0cm} L{2.8cm} *{1}{X}}
	& Proficient in: & \emph{Haskell, PureScript, Rust, TypeScript, Python, Clojure/ClojureScript, Java, Dhall, HTML\&CSS\&DOM} \vspace{2 mm}\\
	& Familiar with: & \emph{C, C++, Idris, Bash, Go, Racket, Vala, SQL, PHP, \LaTeX} \vspace{2 mm}\\
	& Tech I use/love: & \emph{Linux, Nix, ZFS, Git, Nginx, Kubernetes, Docker, AWS (S3, EC2, ECS, Lambda, DynamoDB, etc), GCP (GCS, GKE, GCE, Firestore, etc), CI\&CD, PostgreSQL, MySQL, MongoDB, Ansible, Terraform, Django, Servant, NodeJS, Compojure, re-frame, Reagent, ReactJS, AngularJS, BackboneJS, jQuery, Apache Spark...}\\
\end{tabularx}

% SECTION: LANGUAGES
\sectionTitle{Spoken Languages}{\faComments}

\noindent
\large
\begin{tabularx}{\textwidth}{ C{0.0cm} L{3.25cm} *{1}{X}}
	& Mother tongue: & \textbf{Italian}, \textbf{Sardinian} \vspace{2 mm}\\
	& Proficient in: & \textbf{English} (C2 Level. Certification: TOEIC, July 2014. Score: 955/990) \vspace{2 mm}\\
	& Familiar with: & \textbf{Swedish} (A2 Level) \vspace{2 mm}\\
\end{tabularx}

% SECTION: INTERESTS
\sectionTitle{Interests, Memberships \& Achievements}{\faHeart \hspace{0.5mm} \faStar \hspace{0.5mm} \faTrophy}

\noindent
\large
\begin{tabularx}{\textwidth}{ C{0.0cm} L{3.25cm} *{1}{X}}
  & \textbf{Open Source}
    & \href{https://purescript.org}{PureScript Language} Core Team member. Main author and maintainer of \href{https://github.com/spacchetti/spago}{Spago}, the official package manager and build tool. \vvv\\
  & & Core contributor to the \href{https://github.com/dhall-lang/dhall-lang}{Dhall Language} and \href{https://github.com/dhall-lang/dhall-haskell}{its Haskell compiler}. Author of \href{https://github.com/f-f/dhall-clj}{its Clojure compiler} and maintainer of \href{https://github.com/dhall-lang/dhall-kubernetes}{its Kubernetes integration}. \vvv\\
  & & Core contributor to Snake (\href{https://snake.li}{snake.li}), a privacy-aware, end-to-end encrypted social network. The project is now defunct. \vvv\\

  & \textbf{Public Speaking}
  & \href{https://www.youtube.com/watch?v=kPuGS4_9mRc}{"A package manager? I could write that in a weekend"}, ClojuTRE, Sept 2019\vvv\\
  & & \href{https://www.youtube.com/watch?v=_lMltUNB6Yw}{"Live-coding a Compiler: A Challenge"}, Heart of Clojure, Aug 2019\vvv\\
  & & \href{https://www.youtube.com/watch?v=UHp6nEF5m2o}{"Purely Functional DevOps with Dhall"}, ClojuTRE, Sept 2018\vvv\\

  & \textbf{Music}
    & Algorithmic composer and livecoder, art name \href{https://github.com/f-f/CASSALPOPOLO}{CASSALPOPOLO}. Released the EP \href{https://soundcloud.com/cassalpopolo/sets/arangiu}{Arangiu} in September 2019. \vvv\\
  & & Main composer and producer of the band Lights in The Distance. Released the album \href{https://lightsinthedistance.bandcamp.com/releases}{Through The Needles} in April 2017. \vvv\\

  & \textbf{Communities}
    & Former President of Politecnico Open unix Labs (\href{https://poul.org}{poul.org}), a hackerspace and association of Politecnico di Milano students interested in Linux, hacking and FOSS. \vvv\\
  & & Former Students' Representative for the School of Engineering of Politecnico di Milano. \vvv\\
  & & Former member of "Tower of Hanoi", the Politecnico di Milano Computer Security Team. Its activities included participating in international CTF (Capture The Flag) competitions and organizing the PoliCTF.\\ & & Author of several CTF Challenges, mostly Cryptography. \vvv\\
  & & Member of Mensa Italy since 2014 (\href{https://mensa.org}{mensa.org}) \vvv\\
\end{tabularx}

\end{document}
